Hypertension and microbiome

### 2018-12-31 rrbiome.Rmd
alpha diversity

```{r numbers by group}
dset.species %>%
    group_by(SEX, CURR_SMOKE,  HYPERTENSION, Q57X,
             BL_USE_RX_C09, BL_USE_RX_C03, BL_USE_RX_C07, BL_USE_RX_C08) %>%
    summarise(n = n()) %>%
    arrange(desc(n)) %>%
    kable            
```

@@

```{r numbers by group reduced}
dset.species %>%
     group_by(SEX, CURR_SMOKE,  HYPERTENSION, ANYDRUG, ANYEXERCICE) %>%
    summarise(n = n()) %>%
    arrange(desc(n)) %>%
    kable
```

@@

@@

```{r alpha diversity scatterplot, fig.width=10, fig.height=4, eval = FALSE}
ggplot((dset.alpha %>%
        select(BL_AGE, BMI, SYSTM, DIASM, PULSEPRESSURE, MAP, SEX, diversities_shannon) %>%
        gather(Covariate, Value, -SEX, -diversities_shannon)), 
       aes(x=diversities_shannon, y=Value)) +
    facet_wrap(~Covariate, ncol=4, scales = "free") +
    geom_point(size=0.1, shape=1, aes(colour = SEX)) +
    geom_smooth(method=lm, se=TRUE, size=0.5, color = 'Black') +
    stat_poly_eq(formula = "y ~ x",
                 aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
                 label.y = 0,
                 parse = TRUE,
                 size = 3) +   
    ylim(0, 200) +
    ggplot2::theme_minimal() 
```

@@

```{r lm model, eval = FALSE}
lm(MAP ~ diversities_shannon, data=dset.alpha) %>%
    summary(.) %>% coef %>% kable(., digits=4)
lm(MAP ~ BL_AGE + SEX + diversities_shannon, data=dset.alpha) %>%
    summary(.) %>% coef %>% kable(., digits=4)
lm(MAP ~ BL_AGE + SEX + BMI + CURR_SMOKE + Q57X + diversities_shannon, data=dset.alpha) %>%
    summary(.) %>% coef %>% kable(., digits=4)

>>>>

```{r numbers by group}
dset.species %>%
    group_by(SEX, CURR_SMOKE,  HYPERTENSION, Q57X, DIAB,
             BL_USE_RX_C09, BL_USE_RX_C03, BL_USE_RX_C07, BL_USE_RX_C08) %>%
    summarise(n = n()) %>%
    arrange(desc(n)) %>%
    kable            
```

@@

```{r numbers by group reduced}
dset.species %>%
     group_by(SEX, CURR_SMOKE,  HYPERTENSION, DIAB, ANYDRUG, ANYEXERCICE) %>%
    summarise(n = n()) %>%
    arrange(desc(n)) %>%
    kable
```

@@

Scatterplots for alpha diversity by age group and sex

@@

@@

```{r lm model}
calculateglm <- function(dset,
                         responses = list(model_1 = "MAP", model_2 = "SYSTM", model_3 = "DIASM",
                                          model_4 = "PULSEPRESSURE", model_5 = "HYPERTENSION"),
                         min_n_for_continuous = 10,
                         modelstring = "%s ~ AGE + sex") {
    glmlist <- lapply(responses, function(response) {
        fo.family <- ifelse(length(unique(pull(dset, response)))>min_n_for_continuous, stats::gaussian, stats::binomial)
        fo <- sprintf(modelstring, response)
        stats::glm(formula = as.formula(fo), family = fo.family, data = dset) %>%
            broom::tidy() %>%
                dplyr::filter(grepl("diversities_", term)) %>%
                dplyr::mutate(response = response, fo = fo) %>%
                dplyr::select(-term)
    })
    data.table::rbindlist(test, id = "model_name") %>%
        as.data.frame %>%
        dplyr::mutate(conf.low = estimate - qnorm(1- 0.05/2) * std.error,
                      conf.high = estimate + qnorm(1- 0.05/2) * std.error)
}

calculateglm(as.data.frame(dset.alpha), modelstring = "%s ~ BL_AGE + SEX + BMI + CURR_SMOKE + Q57X + DIAB + BL_USE_RX_C03 + BL_USE_RX_C07 + BL_USE_RX_C08 + BL_USE_RX_C09  + diversities_shannon") %>%
    select(response, estimate, conf.low, conf.high, p.value) %>%
    kable

#lm(MAP ~ BL_AGE + SEX + BMI + CURR_SMOKE + Q57X + DIAB + BL_USE_RX_C03 + BL_USE_RX_C07 + BL_USE_RX_C08 + BL_USE_RX_C09  + diversities_shannon, data = dset.alpha) %>% summary()

###%>% kable(., digits=4)
